Papers

### 2025-07-20 papers.qmd
Update content in papers.qmd and software.qmd
Revised the text in papers.qmd to clarify the reference to Google Scholar and arXiv. Simplified the statement in software.qmd regarding GitHub for consistency and brevity.

*For the most up-to-date and complete list, see [Google Scholar](https://scholar.google.com/citations?user=xT19Jc0AAAAJ&hl=en) or [arXiv](https://arxiv.org/search/?query=bin+yu&searchtype=author).*

>>>>

*Also see [Google Scholar](https://scholar.google.com/citations?user=xT19Jc0AAAAJ&hl=en) and [arXiv](https://arxiv.org/search/?query=bin+yu&searchtype=author)*
